The error in Bayesian phylogenetic reconstruction when speciation co-occurs

### 2019-09-05 razzo-discussion.tex
Diminishing returns in ESSes, both figure and text (40x longer MCMC for a decreases of 'ESS < 200' of 50%)

Ideally, our ESSes would all be above the recommended value of 
200 \richel{I predict not all will be above 200, simply due to 
stochasticity}. Also here, we preferred to have more replicates
and a minimum median of 200 over less replicates.

>>>>

Ideally, our ESSes would all be above the recommended value of 
200 \richel{I predict not all will be above 200, simply due to 
stochasticity}. We are aware ESSes can be increased easily by
making the MCMC chain longer. The shape of the ESS distribution
(see figure \ref{fig:esses_cumulative}), however, is disadvantageous
to do so: to reduce the percentage of $ESS < 200$ by fifty percent,
we would have to increase the MCMC chain lengths by a factor of forty.
We invested this run-time in doing more replicates.
